InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-23 paper.tex
changed to newlines

The first image generative model we use is the Stable Diffusion model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.

Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders. Due to its work directly in pixel space, they are very computational expensive. To lower the computational costs, the Stable Diffusion model (v1.5) is applied in a latent space of powerful pretrained autoencoders. This works without losing quality and flexibility. \cite{Rombach_2022_CVPR}

As a second image generative model we use OpenDalle from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}). OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream. This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.

This is done in two steps: 
\begin{enumerate}
	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
\end{enumerate}

@@

We choose the GPT2 model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.

\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
\begin{enumerate}
	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
	\item Discriminative fine-tuning on every specific task.
\end{enumerate}

@@

Another tool to automatically detect generated text is \textbf{GLTR}. It applies different baseline statistical methods to detect generation artifacts. To do so, it needs access to a certain model, for which it can predict, whether the text is likely to be generated. The text is compared with the distribution of next words, in the given context. The tool calculates which word would have been predicted as next word at each token in the text and allows to colour which words are how likely to appear by the model at a given position and context. If a text is coloured completely green, a lot of words have a high chance, that they would have been predicted at this position by e.g. the currently hosted GPT2 117M model. Therefore, it is likely that a mostly green coloured text is generated by the GPT2 model. This approach can also be used for other models. \cite{gehrmann-etal-2019-gltr}

>>>>

The first image generative model we use is the \textbf{Stable Diffusion} model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}. \newline
Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders. Due to its work directly in pixel space, they are very computational expensive. To lower the computational costs, the Stable Diffusion model (v1.5) is applied in a latent space of powerful pretrained autoencoders. This works without losing quality and flexibility. \cite{Rombach_2022_CVPR}

As a second image generative model we use \textbf{OpenDalle} from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}). OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream. This is achieved by training a transformer to autoregressively model those tokens into the resulting stream. \newline
This is done in two steps:

\begin{enumerate}
	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
\end{enumerate}

@@

We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning. \newline 
\cite{radford2018improving} try to avoid this problem in a simple two step procedure:

\begin{enumerate}
	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
	\item Discriminative fine-tuning on every specific task.
\end{enumerate}

@@
